Verifying Demonstrations

### 2020-03-13 paper/ZKPK-instantiations.tex
Changes some equations to display, fixes bugs in eqns
Moves ZKPK instantiations to the appendix

\paragraph*{Instantiations of the \acs{ZKPK} protocols}

For the convenience of the reader, we summarize 
(from~\cite{Camenisch-phdthesis}) how to instantiate general \acp{ZKPK} for 
discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
which, in its original form, can be written as \(\PK[\alpha][A = g^\alpha]\).
The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
    \prod_{i=1}^n g_i^{\alpha_i}]\).
This could equivalently be written as
\begin{equation*}
  \Proto%
  {\PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i]}%
  {\PKverify[\{g_i\}_i, q, A]},
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (\(\top\)) or reject (\(\bot\)).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

@@

For the non-interactive instance, \(\SPK[\alpha][A = g^\alpha][m]\), we use the 
Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.

\begin{figure}
  \small
  \begin{algorithmic}
    \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
      \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \ZZ_q\)}
      \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
      \State{$c \gets H(\{g_i\}_i\concat A\concat R\concat m)$}
      \For{$1\leq i\leq n$}
        \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
      \EndFor{}
      \State{\Return{$(\{s_i\}_i, c)$}}
    \EndFunction{}
  \end{algorithmic}

  \begin{algorithmic}
    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
        \State{\Return{$\top$}}
      \EndIf{}
      \State{\Return{$\bot$}}
    \EndFunction{}
  \end{algorithmic}
  \caption{%
    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
    using the Fiat-Shamir heuristic on the Schnorr identification 
    scheme~\cite{Camenisch-phdthesis}.
  }%
  \label{SPKalgorithms}
\end{figure}

>>>>

\section{Instantiations of the \acs{ZKPK} protocols}%
\label{ZKPK-instantiations}

Following is a brief summary from~\cite{Camenisch-phdthesis} of how to 
instantiate general \acp{ZKPK} for discrete logarithms based on the Schnorr 
identification scheme~\cite{Schnorr}, which, in its original form, can be 
written as \(\PK[\alpha][A = g^\alpha]\).
The generalized form would be \[
  \PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}].
\]
This could equivalently be written as
\begin{equation*}
  \Proto%
  {\PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i]}%
  {\PKverify[\{g_i\}_i, q, A]},
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (\(\top\)) or reject (\(\bot\)).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{multline*}
  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
\end{multline*}
however, the challenge \(c\) must be the same in both sub-protocols.

@@

%For the non-interactive instance, \(\SPK[\alpha][A = g^\alpha][m]\), we use the 
%Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
%illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.
%
%\begin{figure}
%  \small
%  \begin{algorithmic}
%    \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
%      \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \ZZ_q\)}
%      \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
%      \State{$c \gets H(\{g_i\}_i\concat A\concat R\concat m)$}
%      \For{$1\leq i\leq n$}
%        \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
%      \EndFor{}
%      \State{\Return{$(\{s_i\}_i, c)$}}
%    \EndFunction{}
%  \end{algorithmic}
%
%  \begin{algorithmic}
%    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
%      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
%      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
%        \State{\Return{$\top$}}
%      \EndIf{}
%      \State{\Return{$\bot$}}
%    \EndFunction{}
%  \end{algorithmic}
%  \caption{%
%    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
%    using the Fiat-Shamir heuristic on the Schnorr identification 
%    scheme~\cite{Camenisch-phdthesis}.
%  }%
%  \label{SPKalgorithms}
%\end{figure}
